\vspace{-6.0mm}
\cvsection{Research \& Projects}

\begin{cventries}
% \vspace{-1.0mm}

\cvexperience
{\entrylocationstyle{DAG analysis of 2018 Alibaba Trace
}，Wei Wang}
{12/2018 - PRESENT}
{
    \begin{cvitems}
    \item {Analyze the trace using Spark SQL.}
    \item {Generate DAGs of queries from TPC-H and TPC-DS.}
    \item {Do regression analysis to learn what influenced the run time of batch jobs.}
    \end{cvitems}
}

\cvexperience
{\entrylocationstyle{Load Balance for Structured Data
}，Wei Wang}
{12/2018 - PRESENT}
{
    \begin{cvitems}
    \item {Do controlled experiments to learn the effects of data shuffling on small clusters.}
    \item {Implement the prototype on alluxio.}
    \end{cvitems}
}

\cvexperience
{\entrylocationstyle{Heavy Hitters Detection}，Qingjun Xiao}
{09/2017 - 04/2018}
{
    \begin{cvitems}
    \item {I read papers about hash, DCN, heavy hitter detection, virtual switch and so on.}
    \item {I tried to write C/C++ codes about heavy hitter detection in those papers.}
    \item {I get used to reading English papers and learn to search for my study.}
    \end{cvitems}
}

\cvexperience
{\entrylocationstyle{Advertising Management System}，Group member}
{08/2017 - 09/2017}
{
    \begin{cvitems}
    \item {Our team developed a charging management system for customers who advertised on web pages. My part was in frontend, where I used ECharts to visualize data from backend.}
    \item {Our team got an award for project management. Meanwhile, I got to know, as the number of members in a team increased, the cost of communication increased a lot.}
    \end{cvitems}
}

\cvexperience
{\entrylocationstyle{Talent APP}，Group Member}
{06/2017 - 07/2017}
{
    \begin{cvitems}
    \item {This was a platform where talents at school could give special courses and other students could pay to attend these courses. I was in the Android team.}
    \item {As our team was startup, I got to know something such as design, development and marketing.}
    \end{cvitems}
}

 \cvexperience
 {\entrylocationstyle{Application Development and Low-power Management Based On RFID Tags With Sensors and Wireless Charging.}}
 {12/2016 - 12/2017}
 {
     \begin{cvitems}
     \item {I learnt machine learning by myself and I gave some presentations to my team.}
     \item {Our team collected data of movements from accelerometer on RFID tags and sent it to a PC for training and testing. The accuracy was around 90\%.}
     \end{cvitems}
 }
\end{cventries}